\cvsection{Publications}

\begin{cventries}
  \cventry
    {} % Empty position
    {} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      %\begin{enumerate}[leftmargin=2ex, nosep, noitemsep]
        \item {McDaniel, M., \& Baird, A. (2019, July). \textit{A Full-Body Model of Burn Pathophysiology and Treatment Using the BioGears Engine.} In 2019 41st Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) (pp. 261-264). IEEE.}
        \item {McDaniel, M., Keller, J., White, S., \& Baird, A. (2019). \textit{A Whole-Body Mathematical Model of Sepsis Progression and Treatment Designed in the BioGears Physiology Engine.} Frontiers in physiology, 10, 1321.}
        \item{McDaniel, M., Carter, J., Keller, J. M., White, S. A., \& Baird, A. (2019). \textit{Open source pharmacokinetic/pharmacodynamic framework: tutorial on the BioGears Engine.} CPT: pharmacometrics \& systems pharmacology, 8(1), 12-25.}
        \item{Battista, N. A., Baird, A. J., \& Miller, L. A. (2015). \textit{A mathematical model and MATLAB code for muscle–fluid–structure simulations.} Integrative and comparative biology, 55(5), 901-911.}
        \item{Baird, A., Waldrop, L., \& Miller, L. (2015). \textit{Neuromechanical pumping: boundary flexibility and traveling depolarization waves drive flow within valveless, tubular hearts.} Japan Journal of Industrial and Applied Mathematics, 32(3), 829-846.}
        \item{ Baird, A. (2014). \textit{Modeling Valveless Pumping Mechanisms.}}
        \item{ Baird, A., King, T., \& Miller, L. A. (2014). \textit{Numerical study of scaling effects in peristalsis and dynamic suction pumping.} Contemp. Math, 628, 129-148.}
        \item{Baird, A., \& Miller, L. (2013, November). \textit{Electro-dynamic suction pumping at small scales.} In APS Division of Fluid Dynamics Meeting Abstracts.}
      %\end{enumerate}
      \end{cvitems}
    }
\end{cventries}
\pagebreak